Neural dialogue act tagging with transformer pre-training (or something like that...)

### 2019-04-05 abstract.tex
experiments
some experimens

\section{Model}
\begin{itemize}
  \item We use a simple RNN to pass encode discourse context between utterances and predict dialogue act labels.
  \item At each time step, the 
\end{itemize}

\section{Experiments}

>>>>

\section{Model}
The proposed model has two components: an utterance encoder, and a sequence model that predicts the dialogue act tag.
For the sequence model, we use a simple RNN.
Conceptually the hidden state of this RNN represents the discourse context which, 
together with the encoded utterance, is used to predict the discourse act tag.

\section{Experiments}
Our aim is to test the effectiveness of different utterance encoding schemas. 
\begin{enumerate}
  \item Average word embedding (word2vec)
  \item CNN (with/without word2vec initalization)
  \item BERT encoded sentences (with/without additional unsupervised pretraining)
  \item Average BERT word embeddings
\end{enumerate}
